Ancestry linkage in hybrid zones

### 2016-02-16 drafts/hybrid_zone.tex
yb wrote more discussion

\subsection{Additional signatures around selected loci}

@@

\subsection{Paths to inference}
Our results suggest that a few natural statistical summaries could help identify selected loci in hybrid zones. 
Specifically, a novel statistic, $l_I(m)$ -- the genetic length of ancestry surrounding a site of a given lineage -- could prove a simple and informative summary. 
This statistic, perhaps in relation to the length of ancestry around adjacent sites, could be developed into an approach to stand genomes from hybrid zones to identify putatively selected loci. \alisa{While numerical solutions of the PDEs presented here may be computationally restrictive, with some simplifying approximations, it is possible that a future framework could be constructed for inference of migration rate, hybrid zone age and selection.??}

\subsection{Assumptions}
We made numerous simplifying assumptions to derive our analytical and also in the execution of the simulations. %Thus before our results can be profitably used for inference, it is worthwhile to  reflect on our assumptions and their consequences. 
Foremost, we have assumed that selection acts against heterozygotes, and that there is a single underdominant locus. This situation is rare in nature, since underdominant loci cannot invade when rare, and thus this assumption is likely rarely met. \alisa{We believe, however, that this assumption is unlikely to drastically influence our results, and previous results demonstrating that underdominant loci shares similar properties as more realistic genetic models such as ecological selection, mean that our findings here are somewhat generalizable} \citep{Barton1989; Barton1993}

@@

Lastly, the analytic model presented here lacks coalescence. \alisa{This can result in an underestimate of covariance in ancestry, as we have ignored sharing through genealogy \cite{Liang2014}.} The broad agreement between our analytic predictions and simulations suggests that this assumption does not impact our general results.

@@

\subsection{Future directions}

Some words about how confidently calling tracts is the way of the future.\\
How can this be applied to detecting selection?

>>>>

\subsection*{Additional signatures around selected loci}

@@

\subsection*{Paths to inference}
Our results suggest that a few natural statistical summaries could help identify selected loci in hybrid zones. 
Specifically, a novel statistic, $l_I(m)$ -- the genetic length of ancestry surrounding a site of a given lineage -- could prove a simple and informative summary. 
This statistic, perhaps in relation to the length of ancestry around adjacent sites, could be developed into an approach to stand genomes from hybrid zones to identify putatively selected loci. \alisa{While numerical solutions of the PDEs presented here may be computationally restrictive, with some simplifying approximations, it is possible that a future framework could be constructed for inference of migration rate, hybrid zone age and selection.??}

\subsection*{Assumptions}
We made numerous simplifying assumptions to derive our analytical and also in the execution of the simulations. %Thus before our results can be profitably used for inference, it is worthwhile to  reflect on our assumptions and their consequences. 
Foremost, we have assumed that selection acts against heterozygotes, and that there is a single underdominant locus. This situation is rare in nature, since underdominant loci cannot invade when rare, and thus this assumption is likely rarely met. \alisa{We believe, however, that this assumption is unlikely to drastically influence our results, and previous results demonstrating that underdominant loci shares similar properties as more realistic genetic models such as ecological selection, mean that our findings here are somewhat generalizable} \citep{Barton1989; Barton1993}

@@

Lastly, the analytic model presented here lacks \yb{both coalescence and a true pedigree structure}. \alisa{This can result in an underestimate of covariance in ancestry, as we have ignored sharing through genealogy \cite{Liang2014}.} 
The broad agreement between our analytic predictions and simulations that includee an explicit pefdigree structure suggests that this assumption does not have a sever qualitative impact on our major results.

@@

\subsection*{Future directions}
Our work has highlighted distinct genomic signatures accompanying hybrid incompatibilities. 
We suggest that such signatures could be combined in an inference framework that aims to identify incompatibilities from genome scans of hybrid zones.  
However, doing so requires careful evaluation of potential signals of an incompatibility. 
For example, should we consider jointly lengths of ancestry and allele frequencies to identify incompatibilities?
Will dividing haplotype length by the length of adjacent haplotypes add power to tests because of the extra information contained in this measure, or add noise because of chance variation in these statistics.  
Validation of the effectiveness of our proposed statistics, especially under demographic models that differ from the one dimensional hybrid zone explored above, will  provide a guide on how our results can be used to learn about selection from the distribution of ancestry tract lengths.

Throughout, we focussed on hybrid incompatibilities, however, the possibility that some loci adaptively introgress across hybrid zones has excited many biologists \yb{(CITE: M.L. Arnold Transfer and origin of adaptations through natural hybridization: Were Anderson and Stebbins right? Plant Cell, 16 (2004), pp. 562?570)}.   
The best characterized example of adaptive introgression comes from the vitamin K epoxide reductase subcomponent 1 (vkorc1), which seems to have spread from Algerian mice \emph{Mus spretus} to house mice \emph{Mus musculus} from because it confers resistance to the anticoagulant rodenticide, warfarin .\yb{CITE http://www.sciencedirect.com/science/article/pii/S0960982211007160}. 
Future work could dress expected genomic signatures of adaptive introgression in hybridizing populations using the number and length of haplotypes of non-native ancestry. 
Doing so requires an understanding of how positive selection shapes ancestry block lengths in these cases.

\subsection*{Conclusion}
SOMETHING AWESOME
